Open archaeology, open source?

### 2024-04-15 analysis/_99-appendices.qmd
Minor fix to appendix.

The impetus for this work was a session at the Computer Applications and Quantitative Methods in Archaeology (CAA) virtual annual meeting in Cyprus in June 2021.
Our thanks to Martin Hinz, Clemens Schmid, Sophie Schmidt and other members of the 'scientific scripting languages in archaeology (CAA-SSLA, <https://sslarch.github.io/>) for organizing the session and encouraging us to develop the work further.

@@

<!-- TODO: Zack: anything to add? -->

>>>>

The impetus for this work was a session at the Computer Applications and Quantitative Methods in Archaeology (CAA) virtual annual meeting in Cyprus in June 2021.
Our thanks to Martin Hinz, Clemens Schmid, Sophie Schmidt and other members of the Scientific Scripting Languages in Archaeology Special Interest Group (CAA-SSLA, <https://sslarch.github.io/>) for organizing the session and encouraging us to develop the work further.

@@
